---
output: 
  word_document:
    reference_docx: "phs-offstats-summary.docx"
    fig_caption: no
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi = 300)
library(ggplot2)
library(here)
library(openxlsx)
library(dplyr)
library(tidyr)
library(officer)
library(janitor)
library(flextable) # takes ages to load

# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# 
# N.B. Could not get table formatted sufficiently well. 
# Had to reduce flextable width from 1.26 to 0.9 to fit on portrait page. 
# But this means column heading text wrapping over three lines, 
# not very readable. And landscape format not working either. 
# Therefore, best to simply use the script:
# ../summary_publication/generate_summary_in_excel.R 
#
# N.B. throughout the text that will be seen by the reader, 
# I have added "???" in all places where manual editing will be needed. 
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

# source() doesn't seem to work,  
# so copy the function to create the table here instead
# source("code/functions.R")

# copied from functions.R
make_summary_table <- function() {
  # Import the summary data 
  # from the separate file containing rows from HB_hosp where Location is Scotland 
  scotland_performance_all_qpis <- readWorkbook(here("for_summary_table", "Scotland_rows_no_comments.xlsx"))
  
  # Add target status column called Result
  scotland_performance_all_qpis <- scotland_performance_all_qpis |>
    mutate(Result = ifelse(RAG_Status == 1, "Target met", "Target not met")) |>
    mutate("Performance (%)" = round_half_up(PerPerformance, digits = 1)) |>
    rename("Target" = Target_Label)
  
  # Use pivot_wider to create columns for the years
  # Needs more work, to add target status column
  performance_by_year <- scotland_performance_all_qpis |>
    pivot_wider(names_from = Cyear, 
                values_from = c("Performance (%)", Result),
                id_cols = c(QPI,Target), 
                names_sep = " ",
                names_vary = "slowest"
    ) 
  
  return(performance_by_year)
}



```

<Div custom-style = "Publication Title">I have added ??? in all places where manual editing will be needed.
TSG??? cancer QPIs YYYY??? to YYYY??? Summary Publication</Div>
<Div custom-style = "Publication subtitle">Patients diagnosed from Month/YYYY??? to Month/YYYY???</Div>
<Div custom-style = "Stats designation">An Official statistics release for Scotland</Div>
<Div custom-style = "Publication date">Publication date: DD Month YYYY???</Div>
<Div custom-style = "Restricted Stats">Unduly RESTRICTED STATISTICS: embargoed to 09:30 dd/mm/yyyy???</Div>

# About this release
This release by Public Health Scotland (PHS) presents performance against the National 
TSG??? Quality Performance Indicators (QPIs) in the Cancer QPIs dashboard held within the 
Scottish Cancer Registry and Intelligence Service (SCRIS).

# Main Points
???Proin nec ultricies dolor. Maecenas pulvinar, enim et imperdiet cursus, mi

<Div custom-style = "Bullet 1">Maecenas ut sagittis mi. Vestibulum faucibus ligula sit amet facilisis pulvinar. Morbi mollis odio id est consequat, a convallis quam finibus. Morbi id congue turpis, sit amet ultrices tortor. Phasellus vel nisi. There were ??? patients diagnosed etc... ???</Div>
<Div custom-style = "Bullet 1">Quisque iaculis congue aliquet. Aenean in dictum nisl. Etiam quis ullamcorper ex. Aenean mollis ante eget.??? At Scotland-level, the target was met for ??? of ??? targets ???</Div>



```{r flextable-table-data, ft.align = "left"}
# Set up some formatting for flextable to be applied to most tables
my_ft_format <- function(ft) {
  ft |>
    bold(part = "header") |>
    bg(bg = "#43358B", part = "header") |>
    color(color = "white", part = "header") |>
    align(align = "left", part = "header") |>
    valign(valign = "center", part = "header") |>
    valign(valign = "top", part = "body") |>
    colformat_num(big.mark = "") |>
    fontsize(size = 12, part = "all") |>
    border(border = fp_border_default(color = "#000000", width = 0.5),
           part = "all")
}


```

<br>  
<!---BLOCK_LANDSCAPE_START{break_page: "nextPage"}--->
<Div custom-style = "Table or chart caption">Percentage performance against Quality Performance Indicators
Is this table unformattable???</Div>
  

```{r qpi_summary_table}
# Add the QPI summary table
summary_table_for_Rmd <- make_summary_table()

headings <- names(summary_table_for_Rmd)

flextable(summary_table_for_Rmd, theme_fun = NULL) |>
  my_ft_format() |>
  set_header_labels(values = headings) |>
  bold(i = nrow(summary_table_for_Rmd)) |>
  align(j = 2, align = "right", part = "body") |>
  height(height = 0.236, part = "body") |>
  hrule(rule = "atleast", part = "body") |>
  width(width = 0.9)
```
<!---BLOCK_LANDSCAPE_STOP{break_page: "nextPage"}--->

# Background
National cancer quality performance indicators have been developed to support continuous 
quality improvement in cancer care ([CEL 06 2012](https://www.sehd.scot.nhs.uk/mels/CEL2012_06.pdf)). 
NHS Boards are required to report these 
indicators against a clinically agreed indicator specific target as part of the mandatory national 
cancer quality programme. They have been developed collaboratively by 
[North Cancer Alliance](https://www.nhsscotlandnorth.scot/nca/), 
[South East Scotland Cancer Network](http://www.scan.scot.nhs.uk/), 
[West of Scotland Cancer Network](http://www.woscan.scot.nhs.uk/), 
[Healthcare Improvement Scotland](https://www.healthcareimprovementscotland.scot/) 
and PHS. Figures are gathered and recorded in the central 
database by specialised cancer audit teams in the cancer networks.

# Contact
Garry Hecht | Principal Information Analyst | [phs.cancerstats@phs.scot](mailto:phs.cancerstats@phs.scot)

Pauline Ward | Information Analyst | [phs.cancerstats@phs.scot](mailto:phs.cancerstats@phs.scot)

For all media enquiries please email [phs.comms@phs.scot](mailto:phs.comms@phs.scot) or call 0131 275 6105.

# Further information
Data from this publication are available from the [publication page](https://publichealthscotland.scot/publications/YOUR-PUBLICATION-URL) on our website.

Open data from this publication is available as an Excel file to download from the publication page.

Our statistical practice is regulated by the Office for Statistics Regulation (OSR).

dashboard access etc???

Visit our website for [further information about our statistics and PHS as an Official Statistics producer.](https://publichealthscotland.scot/our-organisation/about-our-statistics/official-statistics/)

The next release of this publication will be DD Month YYYY???.

Other formats of this publication are available on request by calling 0131 314 5300 or emailing [phs.otherformats@phs.scot](mailto:phs.otherformats@phs.scot).

