---
output: 
  word_document:
    reference_docx: "phs-offstats-summary.docx"
    fig_caption: no
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi = 300)
library(ggplot2)
library(here)
library(openxlsx)
library(dplyr)
library(tidyr)
library(officer)
library(janitor)
library(flextable) # takes ages to load

# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# N.B. throughout the text that will be seen by the reader, 
# I have added "???" in all places where manual editing will be needed. 
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

# source doesn't seem to work  
# so copy the function to create the table here instead
# source("code/functions.R")

# copied from functions.R
make_summary_table <- function() {
  # Import the summary data 
  # from the separate file containing rows from HB_hosp where Location is Scotland 
  scotland_performance_all_qpis <- readWorkbook(here("for_summary_table", "Scotland_rows_no_comments.xlsx"))
  
  # Add target status column called Result
  scotland_performance_all_qpis <- scotland_performance_all_qpis |>
    mutate(Result = ifelse(RAG_Status == 1, "Target met", "Target not met")) |>
    mutate("Performance (%)" = round_half_up(PerPerformance, digits = 1))
  
  # Use pivot_wider to create columns for the years
  # Needs more work, to add target status column
  performance_by_year <- scotland_performance_all_qpis |>
    pivot_wider(names_from = Cyear, 
                values_from = c("Performance (%)", Result),
                id_cols = QPI,
                names_sep = " ",
                names_vary = "slowest"
                ) 
  
  return(performance_by_year)
  
}



```

<Div custom-style = "Publication Title">(TSG???) cancer QPIs YYYY??? to YYYY??? Summary Publication</Div>
<Div custom-style = "Publication subtitle">Patients diagnosed from Month/YYYY??? to Month/YYYY???</Div>
<Div custom-style = "Stats designation">An Official statistics release for Scotland</Div>
<Div custom-style = "Publication date">Publication date: DD Month YYYY???</Div>
<Div custom-style = "Restricted Stats">Unduly RESTRICTED STATISTICS: embargoed to 09:30 dd/mm/yyyy???</Div>

# About this release
This release by Public Health Scotland (PHS) presents performance against the National 
(TSG)??? Quality Performance Indicators (QPIs) in the Cancer QPIs dashboard held within the 
Scottish Cancer Registry and Intelligence Service (SCRIS).

# Main Points
???Proin nec ultricies dolor. Maecenas pulvinar, enim et imperdiet cursus, mi

<Div custom-style = "Bullet 1">Maecenas ut sagittis mi. Vestibulum faucibus ligula sit amet facilisis pulvinar. Morbi mollis odio id est consequat, a convallis quam finibus. Morbi id congue turpis, sit amet ultrices tortor. Phasellus vel nisi. There were ??? patients diagnosed etc... ???</Div>
<Div custom-style = "Bullet 1">Quisque iaculis congue aliquet. Aenean in dictum nisl. Etiam quis ullamcorper ex. Aenean mollis ante eget.??? At Scotland-level, the target was met for ??? of ??? targets ???</Div>

<Div custom-style = "Table or chart caption">Percentage performance against Quality Performance Indicators</Div>
```{r flextable-table-data, ft.align = "left"}
# Set up some formatting for flextable to be applied to most tables
my_ft_format <- function(ft) {
  ft |>
    bold(part = "header") |>
    bg(bg = "#43358B", part = "header") |>
    color(color = "white", part = "header") |>
    align(align = "left", part = "header") |>
    valign(valign = "center", part = "header") |>
    valign(valign = "top", part = "body") |>
    colformat_num(big.mark = "") |>
    fontsize(size = 12, part = "all") |>
    border(border = fp_border_default(color = "#000000", width = 0.5),
           part = "all")
}


```

  
  

```{r qpi_summary_table}
summary_table_for_Rmd <- make_summary_table()

headings <- names(summary_table_for_Rmd)

flextable(summary_table_for_Rmd, theme_fun = NULL) |>
  my_ft_format() |>
  set_header_labels(values = headings) |>
  bold(i = nrow(summary_table_for_Rmd)) |>
  align(j = 2, align = "right", part = "body") |>
  height(height = 0.236, part = "body") |>
  hrule(rule = "atleast", part = "body") |>
  width(width = 1.26)
```

<br>



Maecenas bibendum consequat vehicula. Fusce id viverra lorem, et

<Div custom-style = "Bullet 1">Curabitur luctus luctus lorem, at commodo mauris rutrum quis. Mauris aliquet turpis vel magna bibendum hendrerit. Nulla finibus porta sapien ut pretium. Aliquam elementum mauris.</Div>
<Div custom-style = "Bullet 1">Vivamus bibendum ut tellus rhoncus porttitor. Nam id nibh et.</Div>
<Div custom-style = "Bullet 1">Ut in dapibus massa, ut gravida ligula. Vestibulum ut consectetur:</Div>
<Div custom-style = "Bullet 2">Vivamus luctus varius nibh, a scelerisque ex tincidunt non. Etiam dignissim.</Div>
<Div custom-style = "Bullet 2">Curabitur laoreet viverra magna eget dapibus. Maecenas scelerisque euismod mattis. Sed cursus.</Div>
<Div custom-style = "Bullet 2">Sed in iaculis lectus, sed fermentum urna. Donec efficitur diam eu ipsum viverra, eu ornare justo mollis. Phasellus in dictum tellus.</Div>

# Background
Aliquam sed maximus ante, a imperdiet est. Vivamus vel diam facilisis, pulvinar erat consequat, consequat nulla. Praesent lorem dolor, luctus ut libero vitae, venenatis congue tortor.

Nunc at mauris euismod, mattis tellus sed, vehicula dolor. Duis quis auctor elit. Fusce eu dui eu magna convallis porttitor in ac purus. Proin sed tellus massa. In pulvinar augue sit amet faucibus maximus. Aenean porttitor arcu vitae lacus fringilla condimentum. Praesent laoreet, felis non dignissim viverra, libero nunc eleifend sapien, sed dignissim felis risus et tellus.

# Contact
Garry Hecht | Principal Information Analyst | [phs.cancerstats@phs.scot](mailto:phs.cancerstats@phs.scot)

Pauline Ward | Information Analyst | [phs.cancerstats@phs.scot](mailto:phs.cancerstats@phs.scot)

For all media enquiries please email [phs.comms@phs.scot](mailto:phs.comms@phs.scot) or call 0131 275 6105.

# Further information
Data from this publication are available from the [publication page](https://publichealthscotland.scot/publications/YOUR-PUBLICATION-URL) on our website.

Open data from this publication is available as an Excel file to download from the publication page.

Our statistical practice is regulated by the Office for Statistics Regulation (OSR).

Visit our website for [further information about our statistics and PHS as an Official Statistics producer.](https://publichealthscotland.scot/our-organisation/about-our-statistics/official-statistics/)

The next release of this publication will be DD Month YYYY.

Other formats of this publication are available on request by calling 0131 314 5300 or emailing [phs.otherformats@phs.scot](mailto:phs.otherformats@phs.scot).

